Ethnicity sensitive author disambiguation using semi-supervised learning

### 2016-04-29 paper/author_disambiguation.tex
A few words about ethnicity dataset

Overall, these results all encourage further improvements and research. For
blocking, one of the challenges is to manage signatures with inconsistent
surnames or first given names (cases 4 and 5, as described in
Section~\ref{methods:blocking}) while maintaining blocks to a tractable size.
As phonetic algorithms are not yet perfect, another direction  for further work is the design of better
phonetization functions, tailored for author disambiguation. For the linkage function,
the good results of the proposed features pave the way for further research  in
ethnicity-sensitive author disambiguation. The automatic fitting of the
pipeline to cultures and ethnic groups for which standard author disambiguation
is known to be less efficient (\eg, Chinese authors with many homonyms)  indeed
constitutes a direction of research with great potential benefits for the
concerned scientific communities.

>>>>

Overall, these results all encourage further improvements and research. Because of the sensitivity of name-to-ethnicity data, it was not easy to obtain a sufficient coverage of names and ethnicities in the dataset. Even though, we observed some performance enhancements with the generated ethnicity estimator. This motivates working on building a better name-to-ethnicity dataset and measuring its impact on the performance. For
blocking, one of the challenges is to manage signatures with inconsistent
surnames or first given names (cases 4 and 5, as described in
Section~\ref{methods:blocking}) while maintaining blocks to a tractable size.
As phonetic algorithms are not yet perfect, another direction  for further work is the design of better
phonetization functions, tailored for author disambiguation. For the linkage function,
the good results of the proposed features pave the way for further research  in
ethnicity-sensitive author disambiguation. The automatic fitting of the
pipeline to cultures and ethnic groups for which standard author disambiguation
is known to be less efficient (\eg, Chinese authors with many homonyms)  indeed
constitutes a direction of research with great potential benefits for the
concerned scientific communities.
